DATA 624 Homework 1

### 2020-02-08 DATA624/HW1.Rmd
Updated HW1

@@

**There appears to be a monthly pattern to the data.**

@@

```{r}
autoplot(gasoline)
ggseasonplot(gasoline)
#ggsubseriesplot(gasoline)
gglagplot(gasoline)
ggAcf(gasoline)
```

@@

>>>>

**It stacks the visualization instead of having small multiples.**

@@

**There appears to be a seasonal pattern to the data.**

@@

```{r}
autoplot(gasoline)
ggseasonplot(gasoline)
gasoline %>%
  as.vector()%>%
  ts(., frequency=52) %>%
  ggsubseriesplot()
gglagplot(gasoline)
ggAcf(gasoline)
```

**There is a trend and some seasonality to the data.  I thought you would see some cyclical behavior coinsiding with U.S. regression dates but that is not present.**

@@

**The trend of the supply of gasoline has been generally increasing.  It increases slightly during the summer months.**
